---
title: "Plotly Assignment - Mustaf.R"
author: "Jeff Ball"
date: "December 23, 2016"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r Initialize, echo=FALSE}
	suppressWarnings(suppressMessages(library(plotly)))
```

## Plotly Interactive Graph

In honor of the new movie *Rogue One* this simple interactive graph allows someone to zoom in on what appears to be a lava planet.  For this demonstration, I'll call it "Mustaf" and the function is contained in a file called "Mustaf.R"

The 3D plot creates 500 random points in 7 different layers.  The user can rotate as well as zoom in and zoom out.  For purposes of this assignment the code to draw the plot is shown on the second slide; the interactive graph is on the third slide.

## The Code

```{r createPoints,echo=FALSE}
	layers <- 7		# number of layers
	np <- 500		# number of points for each sphere

	for (i in 1:layers)
	{
		r <- i * 5	# radius will grow in increments of 5
	
#	create random points for each layer...

		angleInc <- runif(np,min=0,max=pi)		# inclination
		angleAzm <- runif(np,min=0,max=2*pi)	# azimuth
		xa <- r * sin(angleInc) * cos(angleAzm)	
		ya <- r * sin(angleInc) * sin(angleAzm)
		za <- r * cos(angleInc)
		ca <- rep(i,times=np)

#	bring the vectors together...

		if (i==1)
		{
			x <- xa
			y <- ya
			z <- za
			c <- ca
		}
		else
		{
			x <- c(x,xa)
			y <- c(y,ya)
			z <- c(z,za)
			c <- c(c,ca)
		}
	}

	df <- data.frame(x,y,z,c)
```

```{r plot3D,echo=TRUE,eval=FALSE}
	plot_ly(df,x=~x,y=~y,z=~z,type="scatter3d",
		mode="markers",
		color=~c,
#		colors="GnBu") %>%	    # use this for Dagobah
#		colors="Blues") %>%	    # use this for Kamino
		colors="YlOrRd") %>%	# use this for Mustafar
#		colors="Greys") %>%	    # use this for Hoth
	layout(plot_bgcolor="black") %>%
	layout(paper_bgcolor="black")
```
Note that there is preceding code to generate the 500 random points for each layer by using a RUNIF() function to get a random inclination and azimuth, and then transforming those into x,y,z coordinates.

## The Plot

```{r ShowPlot3D,echo=FALSE,eval=TRUE}
	plot_ly(df,x=~x,y=~y,z=~z,type="scatter3d",
		mode="markers",
		color=~c,
#		colors="GnBu") %>%	    # use this for Dagobah
#		colors="Blues") %>%	    # use this for Kamino
		colors="YlOrRd") %>%	# use this for Mustafar
#		colors="Greys") %>%	    # use this for Hoth
	layout(plot_bgcolor="black") %>%
	layout(paper_bgcolor="black")
```
The 'zoom' function may be different depending on your configuration.  For me, it works when I press the scroll button (middle button) on the mouse.

## The End

Thanks for your time.
